prolfqua - An R-package for Analysing Proteomics Label Free Quantification Experiments

### 2022-03-18 inst/MyArticle/paper.Rmd
Add sticker

x <- dplyr::inner_join(imp, proda, by = c("contrast","protein_Id", "TP", "species"), suffix = c(".imp",".proda"))
ggplot2::ggplot(x,ggplot2::aes( x = diff.imp, y = diff.proda) ) + ggplot2::geom_point() + ggplot2::facet_wrap(~contrast + species) + ggplot2::geom_hline(yintercept = 0, color="red") + ggplot2::geom_vline(xintercept = 0, color="red")

@@

>>>>

x <- dplyr::inner_join(imp, proda, by = c("contrast","protein_Id", "TP", "species"), suffix = c(".imp",".proda"))
ggplot2::ggplot(x,ggplot2::aes( x = diff.imp, y = diff.proda) ) + ggplot2::geom_point() + ggplot2::facet_wrap(~contrast + species) + ggplot2::geom_hline(yintercept = 0, color="red") + ggplot2::geom_vline(xintercept = 0, color="red")
```

@@

## Package sticker

```{r proLFQuaSticker, echo=TRUE, out.height="5cm", eval=TRUE, fig.cap="Sticker maintainer: Witold E. Wolski; License: Creative Commons Attribution CC-BY. Feel free to share and adapt, but don't forget to credit the author."}

file.path(system.file(package = "prolfqua"), 
          "Figures/hexStickerProlfqua.png") |>
  knitr::include_graphics()
```
